Active Learning for Level Set Estimation

### 2013-04-23 ijcai13pres.tex
Initial changes for IJCAI; add ping slide

\author[Alkis Gkotovos]{
\footnotesize
M.Sc. Thesis by Alkis Gkotovos\\
Department of Computer Science\\
ETH Zurich
}

\date[M.Sc. Thesis presentation]{
\footnotesize
Supervised by Prof. Andreas Krause

}

@@

%\pgfdeclareimage[height=0.5cm]{university-logo}{figures/eth_logo_black.pdf}
%\logo{\pgfuseimage{university-logo}}

@@

@@

\begin{frame}
\begin{center}
\large Summary
\end{center}
\vspace{-1em}
\begin{itemize}
\item<1-> \acl algorithm:
\begin{itemize}
\item<2-> \begin{tabular}{m{5.7cm} >{\centering}m{4cm}}Theoretical guarantees & \includegraphics[width=1.3in]{figures/thm.png} \end{tabular}
\item<3-> \begin{tabular}{m{5.7cm} >{\centering}m{4cm}}Competitive with the state-of-the-art in practice (sometimes considerably superior) & \hspace{-0.5em}\includegraphics[width=1.3in]{figures/ev_bgape_seq_long} \end{tabular}
\end{itemize}
\item<4-> Two useful extensions:
\begin{itemize}
\item<5-> \begin{tabular}{m{5.7cm} >{\centering}m{4cm}}Implicit threshold level & \includegraphics[width=1.3in]{figures/limno_bgape_imp_class_140} \end{tabular}
\item<6-> \begin{tabular}{m{5.7cm} >{\centering}m{4cm}}Batch sampling $\rightarrow$ path planning & \includegraphics[width=1.3in]{figures/limno_bgape_pp_30_2} \end{tabular}
\end{itemize}
\item<7-> Look out for algae when swimming in Lake Zurich! {\color{blue}$\ddot\smile$}
\end{itemize}
\end{frame}

>>>>

\author[Alkis Gotovos \emph{et al.}]{
\footnotesize
Alkis Gotovos\inst{1}
\and
Nathalie Casati\inst{1,2}\and
Gregory Hitz\inst{1}\and
Andreas Krause\inst{1}
}

\institute[ETH Zurich]{\inst{1} Department of Computer Science\\ETH Zurich \and %
                      \inst{2} IBM Research -- Zurich}

\date[IJCAI 2013]{
IJCAI 2013
}

@@

%\pgfdeclareimage[height=0.5cm]{eth-logo}{figures/eth-logo.eps}
%\logo{\pgfuseimage{eth-logo}}

@@

\begin{frame}
\begin{center}
\large Geolocating internet latency
\end{center}
\begin{itemize}
\item<1-> Which world regions have low enough latency (e.g. < $150$ ms)
      for video chatting, online gaming, etc.?
\item<2-> Ideal setting for batch sampling $\rightarrow$ multiple pings in parallel
\end{itemize}
\begin{center}
\color{white}
\includegraphics<1-2>[draft,height=2.5in]{figures/map}
\color{black}
\includegraphics<3>[height=2.5in]{figures/map}
\includegraphics<4>[height=2.5in]{figures/map_ls_150}
\end{center}
\end{frame}

@@

\begin{frame}
\begin{center}
\large Summary
\end{center}
\vspace{-1em}
\begin{itemize}
\item<1-> \acl algorithm:
\begin{itemize}
\item<2-> \begin{tabular}{m{5.7cm} >{\centering}m{4cm}}Theoretical guarantees & \includegraphics[width=1.3in]{figures/thm.png} \end{tabular}
\item<3-> \begin{tabular}{m{5.7cm} >{\centering}m{4cm}}Competitive with the state-of-the-art in practice (sometimes considerably superior) & \hspace{-0.5em}\includegraphics[width=1.3in]{figures/ev_bgape_seq_long} \end{tabular}
\end{itemize}
\item<4-> Two useful extensions:
\begin{itemize}
\item<5-> \begin{tabular}{m{5.7cm} >{\centering}m{4cm}}Implicit threshold level & \includegraphics[width=1.3in]{figures/limno_bgape_imp_class_140} \end{tabular}
\item<6-> \begin{tabular}{m{5.7cm} >{\centering}m{4cm}}Batch sampling & \includegraphics[width=1.3in]{figures/limno_bgape_pp_30_2} \end{tabular}
\end{itemize}
\item<7-> Look out for algae when swimming in Lake Zurich! {\color{blue}$\ddot\smile$}
\end{itemize}
\end{frame}
